GO

### 2019-12-12 analysis/12_GO.Rmd
now with markdown headers

@@

@@

@@

@@

@@

>>>>

# Exploring relationships between genes associated with mating behavior, lactation, parental care, and endocrine process in the hypothalamic-pituitary-gonad axis of reproction

## The code

1. Read in list of genes for GO terms: mating beahvior, lactating, parental care, and endocrine process.
2. Read in lists of differentially expressed genes for each transition (e.g. incubation day 17 to hatch) in each tissue (e.g. pituitary)
3. Join the two data frames
4. Print list of differentially expressed genes that correspond to each GO term, separated by either tissue or paretnal stage
5. Repeat the process for a list of candidate genes instead of GO terms.

## GO terms

@@

## Differntially expressed genes by stage for each tissue

@@

## GO and DEGs joined

@@

## Tissue-specifiic differentially expressed genes

@@

## Stage-specific differentially expressed genes

@@

## Candidate genes
